# Shana Green
# R Bridge 
# HW 2
# Due 07/26/20


```{r}

# loading the data set
frostedflakes<- read.csv("frostedflakes.csv")
```

# 1. Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes.

```{r}

#calculating summary stats for all columns of data set

summary(frostedflakes)

#mean

mean(frostedflakes$X, na.rm = TRUE)
mean(frostedflakes$Lab, na.rm = TRUE)
mean(frostedflakes$IA400, ra.rm = TRUE)

#median

median(frostedflakes$X, ra.rm = TRUE)
median(frostedflakes$Lab, ra.rm = TRUE)
median(frostedflakes$IA400, ra.rm = TRUE)

```

# 2. Create a new data frame with a subset of the columns and rows. Make sure to rename it.

```{r}
#Create a subset extracting 50 participants from a given range 

sweetfrostedflakes<-subset(frostedflakes[c(1:50),c("X","Lab","IA400")])
View(sweetfrostedflakes)

```

# 3. Create new column names for the new data frame.

```{r}

colnames(sweetfrostedflakes)<-c("Y","Lab2","JA400")
View(sweetfrostedflakes)

```

# 4. Use the summary function to create an overview of your new data frame. The print the mean and median for the same two attributes. Please compare.

```{r}

summary(sweetfrostedflakes)

#mean

mean(sweetfrostedflakes$Y, na.rm = TRUE)
mean(sweetfrostedflakes$Lab2, na.rm = TRUE)
mean(sweetfrostedflakes$JA400, ra.rm = TRUE)

#median

median(sweetfrostedflakes$Y, na.rm = TRUE)
median(sweetfrostedflakes$Lab2, ra.rm = TRUE)
median(sweetfrostedflakes$JA400, ra.rm = TRUE)


```

```
**frostedflakes$X vs. sweetfrostedflakes$Y**

Mean: frostedflakes$X (50.50) almost doubles the value of sweetfrostedflakes$Y (25.50)

Median: frostedflakes$X (50.50) almost doubles the value of sweetfrostedflakes$Y (25.50)
 
The mean and median are the same for frostedflakes$X (50.50)*
The mean and median are the same for sweetfrostedflakes$Y (25.50)*

**frostedflakes$Lab1 vs. sweetfrostedflakes$Lab2**

Mean: sweetfrostedflakes$Lab2 (37.72) has a slighly higher value than frostedflakes$Lab (37.60) by 0.12

Median: sweetfrostedflakes$Lab2(37.85) has a slightly higher value than frostedflakes$Lab(37.75) by 0.10

**frostedflakes$IA400 vs. sweetfrostedflakes$JA400**

Mean: frostedflakes$IA400 (38.22) has a slighly higher value than sweetfrostedflakes$JA400 (38.13) by 0.09

Median: frostedflakes$IA400(38.50) has a slightly higher value than sweetfrostedflakes$JA400(38.20)  by 0.30

```
# 5. For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”.

```{r}


sweetfrostedflakes$Lab2<-replace(sweetfrostedflakes$Lab2, sweetfrostedflakes$Lab2 > 40, "Corn Flakes")

sweetfrostedflakes

```
```
I chose values over Lab values over 40 and replaced it with string "Corn Flakes"
```

# 6. Display enough rows to see examples of all of steps 1-5 above.

```{r}

head(sweetfrostedflakes,10)



```

# 7. BONUS – place the original .csv in a github file and have R read from the link. This will be a very useful skill as you progress in your data science education and career.

```{r}

frostedflakes<- read.csv("https://raw.githubusercontent.com/sagreen131/R-Week-2/master/frostedflakes.csv")


```